Hydras \& Co.

### 2022-03-18 doc/part-hydras.tex
corrections chapter 6 (up to page 137)

We are now ready to get an exact formula for $L_{\omega^3}$, by diagonalization upon $L_{\omega^2\times i}$.

@@

Crossing a new limit, we prove the following equality: 
$$H'_{\omega^2} (k) = 2 ^ {k+1} \times (k+1) - 1$$.

@@

By well-founded induction on $\alpha$, we prove a simple relation between $L_\alpha$ and $H'\_alpha$.

\emph{From Module~\href{../theories/html/hydras.Epsilon0.L_alpha.html\#H'_L_}{Epsilon0.L\_alpha}}

>>>>

We are now ready to get an exact formula for $L_{\omega^3}$, by diagonalization over $L_{\omega^2\times i}$.

@@

Since $\omega^2$ is a limit ordinal, we prove the following equality: 
\[H'_{\omega^2} (k) = 2 ^ {k+1} \times (k+1) - 1\]

@@

By well-founded induction on $\alpha$, we prove that
 $H'_\alpha(i) \leq L_\alpha(i+1)$ for any $i$.

\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.L_alpha.html\#H'_L_}{Epsilon0.L\_alpha}}
